---
title: "Class Assignment: MPG tables and charts"
author: "Runxin(Daisy) Yu"
date: "September 20, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(knitr)                ## loading the entire knitr package
library(tidyverse)              ## the only tidyverse library you need is ggplot2
library(esquisse)             ## use esquisse to setup the basic plots
knitr::opts_chunk$set(fig.pos = 'H')
library(kableExtra)
library(magrittr)
library(ggplot2)
opts_chunk$set(echo = TRUE)
```

## Class assignment:

Using the MPG dataset, which is available with the ggplot2 library, produce a document that includes the following elements: headers, text, tables, and plots.  

Tables should include a comparison of city and highway mileage by the class of car and the best three car models for city and highway mileage for all the years in which data is available.  

Plot the data displaying as much of the data as you can. Put continuous variables on the axes and include a locally smoothed regression line to show the relationship with mileage.  Also make a box plot comparing city and highway MPG by class of car.  

---
## Tables

This example is flawed even though the code works.  Explain.
And now that you know how to produce the table can you improve the code 
by using an **apply** functional?

---
## Tables
Apply Function
\newline
\newline

```{r echo=FALSE}

data(mpg)     ## load the data

mpg$cyl <- as.factor(mpg$cyl)   ## convert discrete variables to factors so that they plot
mpg$drv <- as.factor(mpg$drv)   ## as different colors, not gradations of one color

mpg$cty <- as.double(mpg$cty)
                                
class <- unique(mpg$class)      ## define a vector for car classes
cty_mean_cls <- round(tapply(mpg$cty,mpg$class,mean),2)
hyw_mean_cls <- round(tapply(mpg$hwy,mpg$class,mean),2)
tb_1 <- cbind(cty_mean_cls,hyw_mean_cls)
cls <- rownames(tb_1)
rownames(tb_1) <- NULL
tb_2 <- cbind(cls,tb_1)
kable(tb_2,digits = 2,
col.names = c("Class", "City", "Highway"), caption = "Mean City and Highway MPG by Car Class",
align = 'c') %>%
  kable_styling(latex_options = 'hold_position',font_size = 15.5,full_width = F,position = "center")%>%
  column_spec(1,bold = T)      
```
## Tables
Aggretate Function
\newline
\newline

```{r, echo = FALSE}

data(mpg)
df1 <- mpg[,c("class","cty","hwy")]
# df1 <- data.frame(Class=mpg$class, City=mpg$cty, Highway=mpg$hwy)
df2 <- aggregate(df1[,2:3],by=list(df1$class),mean)
# df2 <- aggregate(cbind(cty,hwy)~class,data = df1,mean)
kable(df2, digits = 2,                                ## call kable to make the table
      col.names = c("Class", "City", "Highway"), 
      caption = "Mean City and Highway MPG by Car Class" ,align = 'c') %>%
  kable_styling(latex_options = 'hold_position',font_size = 15.5,full_width = F)%>%
  column_spec(1,bold = T)
```
## Tables
Using dyplr
\newline
\newline


```{r echo=FALSE, fig.pos = 'H'}
data(mpg)
mpg$cyl <- as.factor(mpg$cyl)
mpg$drv <- as.factor(mpg$drv)
mpg$cty <- as.double(mpg$cty)

mpg_1 <- select(mpg,cty,hwy,class)

mpg_1 %<>% group_by(class) %>% summarise(City= mean(cty),Highway=mean(hwy)) %>% arrange(class,City,Highway)
kable(mpg_1,digits = 2,
      col.names = c("Class", "City", "Highway"), 
      caption = "Mean City and Highway MPG by Car Class" ,align = 'c') %>%
  kable_styling(latex_options = 'hold_position',font_size = 15.5,full_width = F)%>%
  column_spec(1,bold = T)

```

## Tables
Top 3 MPG Performing Cars in 1999 and 2008
\newline


```{r, echo=FALSE}

options(digits = 3)
cty_mean_08 <- mpg %>% select(model,year,cty,hwy) %>%
    filter(year == 2008) %>%
    group_by(model) %>% summarise(City= mean(cty)) %>% arrange(desc(City)) %>%          head(3)
cty_mean_99 <- mpg %>% select(model,year,cty,hwy) %>%
    filter(year == 1999)%>%
    group_by(model) %>% summarise(City= mean(cty)) %>% arrange(desc(City)) %>%          head(3)
    
hwy_mean_08 <- mpg %>% select(model,year,cty,hwy) %>%
    filter(year == 2008)%>%
    group_by(model) %>% summarise(Highway=mean(hwy)) %>% arrange(desc(Highway))%>%      head(3)
hwy_mean_99 <- mpg %>% select(model,year,cty,hwy) %>%
    filter(year == 1999)%>%
    group_by(model) %>% summarise(Highway=mean(hwy)) %>% arrange(desc(Highway))%>%      head(3)

table_top <- cbind(cty_mean_99,hwy_mean_99,cty_mean_08,hwy_mean_08)
colnames(table_top) <- c('Model', 'Milage', 
                     "Model", "Milage",
                     'Model', 'Milage',
                     "Model", "Milage"
                     )

kable(table_top, digits = 2,booktabs=TRUE,caption = "Top 3 MPG Performing Cars: 1999, 2008",align = 'c') %>% kable_styling(latex_options = 'hold_position',font_size = 15.5,full_width = T)%>%
 add_header_above(c("City 1999"=2, 
                     "Highway 1999"=2,
                     "City 2008"=2,
                     "Highway 2008"=2))

```

## Plot
City 

```{r echo = FALSE}
 ggplot(mpg) +
 aes(x = displ, y = cty) +
 geom_point(aes(color=class),size=2) + geom_smooth() +
 scale_color_hue() +
 theme_minimal(base_size = 16) +
 facet_wrap(vars(year)) + 
  labs(x = "Engine Displacement",y = "City Mileage" ,title = "City MPG by Class of Car: 1999, 2008")

```

## Plot
Highway
```{r echo=FALSE}
ggplot(mpg) +
 aes(x = displ, y = hwy) +
 geom_point(aes(color=class),size=2) + geom_smooth() +
 scale_color_hue() +
 theme_minimal(base_size = 16) +
 facet_wrap(vars(year)) + 
  labs(x = "Engine Displacement", y = "Highway Mileage", title = "Highway MPG by Class of Car: 1999, 2008")

```

## Boxplot
City
```{r echo=FALSE}

ggplot(mpg) +
 aes(x = class, y = cty) +
 geom_boxplot(fill = "#0c4c8a") +
 theme_minimal(base_size=16) +
  labs(x = "Car Class", y = "City Mileage", title = "City MPG by Class of Car: 1999, 2008")
```

## Boxplot
Highway
```{r echo=FALSE}

ggplot(mpg) +
 aes(x = class, y = hwy) +
 geom_boxplot(fill = "#0c4c8a") +
 theme_minimal(base_size=16) +
  labs(x = "Car Class", y = "Highway Mileage", title = "Highway MPG by Class of Car: 1999, 2008")

```

